### 2021-07-09 rad-icfp-2021/relwork.tex

We have introduced a transformation on programs to compute provably efficient (\S\ref{sec:complexity}) 
gradients via reverse derivatives in a purely functional way (\S\ref{sub:Macro for pure reverse mode transformation})
on a simple yet expressive language with functions on arrays (\S\ref{sub:sourcelang}), 
combined with standard functional optimizations (\S\ref{fig:optim}).  
We introduced a novel intermediate representation, Unary Normal Form (\S\ref{sec:unf}) 
to decompose our transformation into simpler transformations.
We gave denotational semantics to our languages and our transformations (\S\ref{sec:correctness}), 
and showed correctness of the reverse-mode translation (\S\ref{sub:Correctness theorem}).
We showed (\S\ref{sec:generalization}) how to lift the restrictions that
we introduced on arrays and how to extend our approach with other constructs such as conditionals.
\clearpage

>>>>

We introduced a transformation on programs to compute provably efficient (\S\ref{sec:complexity}) 
gradients via reverse derivatives in a purely functional way (\S\ref{sub:Macro for pure reverse mode transformation})
on a simple yet expressive language with functions on arrays (\S\ref{sub:sourcelang}), 
combined with standard functional optimizations (\S\ref{fig:optim}).  
We introduced a novel intermediate representation, Unary Normal Form (\S\ref{sec:unf}) 
to decompose our translation into simpler ones.
We gave denotational semantics to our languages (\S\ref{sec:correctness}), 
and proved correctness of the reverse-mode translation (\S\ref{sub:Correctness theorem}).
We showed (\S\ref{sec:generalization}) how to lift the restrictions that
we introduced on arrays and how to extend our approach with other constructs such as conditionals.
\clearpage
